MaxEnt: What is it good for?

### 2015-08-10 ms.tex
Mentioned MaxEnt-as-regulariser

There are some axiomatic arguments supporting MaxEnt
\citep[e.g.][]{shore_johnson, 2006AIPC..872...31C, 2010arXiv1008.4831K},
as well as counterexamples to possible alternatives \citep[e.g.][]{presse}.
However, there is no consensus among Bayesians of the status of MaxEnt: is
it a valid and potentially useful fundamental principle, some kind of an
approximation or computational trick, or a dead end that is solely of
historical interest?

There are several possible reasons for the lack of consensus.

has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (at times, even by Jaynes himself).
Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists, raised on \citet{jaynes},
to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.

>>>>

There are some axiomatic arguments supporting MaxEnt
\citep[e.g.][]{shore_johnson, 2006AIPC..872...31C, 2010arXiv1008.4831K},
as well as counterexamples to possible alternatives \citep[e.g.][]{presse}.
However, there is no consensus among Bayesians about the status of MaxEnt. Is
it a valid and potentially useful fundamental principle, some kind of an
approximation or computational trick, or a dead end that is only of
historical interest?

There are several possible reasons for the lack of consensus. 
One is that the name ``MaxEnt'' has been used to refer not just to the principle
for updating probability distributions, but also to a specific choice of
regularisation term in optimisation-based methods for inverse problems
\citep{}, among other things. Since Bayesian inference is
a more principled way to deal with the uncertainty than regularised
optimisation, this leads to the idea that Bayesian inference
{\it supersedes} MaxEnt, and therefore that MaxEnt can be ignored.

In addition, many defences and explanations of MaxEnt in the literature
are weak.

Consequently, most modern Bayesians pay little attention to the principle,
although there is a tendency among physicists, raised on \citet{jaynes},
to invoke it as a justification
for a prior distribution (be it uniform, exponential, gaussian, or whatever).
The purpose of this article is to explore the principle from the point of
view of a Bayesian practitioner, discuss some of the properties that
make MaxEnt compelling, and propose some ideas about how it could be used in
practice.
